---
format: revealjs
editor: visual
---

```{=html}
<style>
    .reveal .center {
        text-align: center;
        font-size: 3em;
    }
</style>
```

::: center
```         
Visualizing Growth
```
:::

<p style="font-size: 20px;">

*                                            - Saran*

</p>

------------------------------------------------------------------------

##### **Data Definitions & Key Words:**

</br>

<p style="font-size: 14px;">GDP: Gross Domestic Product, measures the total value of goods and services produced in a country within a specific time frame, indicating its economic size and activity.</p>
<p style="font-size: 14px;"> Per-Capita GDP: is the average economic output per person in a country, showing individual wealth on average, basically dividing GDP by population.</p>
<p style="font-size: 14px;"> Purchase Power Parity: adjusts GDP for cost of living differences, reflecting real purchasing power across countries.</p>
<p style="font-size: 14px;"> Inflation: is the increase in prices of goods and services over time, reducing the purchasing power of money.</p>

```{r}
library(tidyverse)
library(vtable)
library(ggplot2)
library(patchwork)
library(readxl)
library(treemap)

data <- read_csv("data/DVdataset.csv")

dataPivot <- pivot_longer(data, cols = starts_with('2'),
                          names_to = "Year",
                          values_to = "Values")


customColors <- c('#d9d9d9', '#99ccff', '#ff9900', '#737373', '#0077cc',
                  '#004066', 'black', "yellow", '#ffd699', '#262626')


dataPivot <- dataPivot %>%
  mutate(Segment = case_when(
    Country %in% c("India", "Russia") ~ "Group1",
    Country %in% c("China", "Japan") ~ "Group2",
    Country %in% c("United Kingdom","Canada" ,"United States",
                   'Germany',"France", "Italy") ~ "Group3"
  ))

```

------------------------------------------------------------------------

##### Which countries contributed most to World's GDP in 2022? And is that all matters?


<p style="font-size: 16px;"> Country's share in global GDP growth, 2022</p>



```{r}
gdpShare <- read_excel("data/gdpShare.xlsx")

gdpShare %>%
  filter(Year == '2022') %>%
  mutate(
    labelsNew = paste0(Country, ": ", round(Values), "%")
  ) %>%
  treemap(
    index = "labelsNew",
    vSize = "Values",
    type = "index",
    algorithm = "squarified",
    palette= "RdBu", # RdYlBu, Set2, RdGy, Pastel2, Spectral, RdBu
    title = "",
    mirror.y = TRUE,
    fontsize.labels = 12
    )

```

------------------------------------------------------------------------

##### 21<sup>st</sup> Century saw US sustain its dominance, while emerging Asian powerhouses China and India surge

<p style="font-size: 16px;">Countries ranked by GDP size</p>



```{r}

legend_order <- c("United States", "China", "Japan", 
                  "Germany", "India", "United Kingdom", 
                  "France", "Russia", "Canada", "Italy")
library(readxl)
pivot3 <- read_excel("data/pivot3.xlsx")

pivot3 %>%
  filter(!(Country %in% c("Mexico", "Spain", "Brazil"))) %>%
  ggplot(aes(x = Year, y = Values, group = Country, color = Country)) +
  
  geom_point(data = . %>% filter(!(Country 
                                   %in% c("United States", "China", "India"))),
             size = 3.5) +
  geom_point(data = . %>% filter(Country 
                                   %in% c("United States", "China", "India")),
             size = 8) +
  geom_smooth(data = . %>% filter(!(Country %in% c("United States", "China", "India"))),
              method = "loess", span = 0.75, se = FALSE, size = 0.5) +
  geom_smooth(data = . %>% filter(Country %in% c("United States", "China", "India")),
            method = "loess", span = 0.75, se = FALSE, size = 1.5) +
  scale_y_reverse() +
  geom_text(data = . %>% filter(Country %in% c("United States", "China", "India")),
            aes(label = Values), 
            vjust = 0.4, size = 3, 
            color = 'white', fontface = 'bold') +
  geom_text(aes(x = 2023, y = 1), color = 'black', label = "United States", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 2), color = 'black', label = "China", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 5), color = 'black', label = "India", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 3, color = 'black'), label = "Japan", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 4, color = 'black'), label = "Germany", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 6, color = 'black'), label = "United Kingdom", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 7, color = 'black'), label = "France", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 8, color = 'black'), label = "Russia", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 9, color = 'black'), label = "Canada", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  geom_text(aes(x = 2023, y = 10, color = 'black'), label = "Italy", 
            hjust = 0, size = 4, check_overlap = TRUE) +
  theme_minimal() +
  scale_color_manual(values = c("United States" = "#CA6702",
                                "China" = "#ff9900",
                                "Japan" = "#E9D8A6",
                                "Germany" = '#A3C4F3',
                                "India" = "#0077cc",
                                "United Kingdom" = "#FDE4CF",
                                "France" = "lightgrey",
                                "Russia" = "#94D2BD",
                                "Italy" = "darkgrey",
                                "Canada" = "#F9C74F")) +
  scale_x_continuous(breaks = c(2001,2011,2022)) +
  theme(
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.title.y = element_text(face = "bold"), 
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_line(size = 2),
        axis.text.x = element_text(size = 10),
        x = NULL,
        y = NULL,
        plot.title = element_text(face = "bold"),
        legend.position = "none"
      ) +
  labs(y = "YEARLY RANKINGS", size = 12)
```

------------------------------------------------------------------------

##### What is their populations? If each country looks so different, is it right to compare by their GDP alone?

<p style="font-size: 16px;">Population trends over the past 2 decades, and current standing</p>

<p style="font-size: 14px;"> Source: IMF's World Economic Outlook, Oct 2023</p>

```{r}

population <- read_csv("data/population.csv")


p5 <- ggplot(population, aes(x = Year, y = id)) +
  geom_ribbon(aes(ymin = l, ymax = h, fill = Country), alpha = 0.6) +
  scale_fill_manual(values = c("United States" = "#CA6702",
                               "China" = "#ff9900",
                               "Japan" = "#E9D8A6",
                               "Germany" = '#A3C4F3',
                               "India" = "#0077cc",
                               "United Kingdom" = "#FDE4CF",
                               "France" = "lightgrey",
                               "Russia" = "#94D2BD",
                               "Italy" = "darkgrey",
                               "Canada" = "#F9C74F")) +
  geom_text(aes(x=2019,y=1650, label = "India"), 
            check_overlap = TRUE, size = 4) +
  geom_text(aes(x=2019,y=2850, label = "China"), 
            check_overlap = TRUE, size = 4) +
  geom_text(aes(x=2019,y=800, label = "United States"), 
            check_overlap = TRUE, size = 4) +
  labs(x = "YEAR", y = "POPULATION (in millions)") +
  scale_x_continuous(breaks = c(2001,2011,2022), limits = c(2001,2025)) +
  scale_y_continuous(breaks = c()) + 
  theme_minimal() +
  theme(axis.title.x = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold"),
        legend.text = element_text(size = 7),
        legend.position = "none",
        axis.ticks.x = element_line(size = 2),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold"),
  ) 


p6 <- population %>%
  filter(Year == 2022) %>%
  ggplot(aes(x = Values, y = reorder(Country, Values), fill = Country)) +
  geom_col(alpha = 0.6) +
  scale_fill_manual(values = c("United States" = "#CA6702",
                               "China" = "#ff9900",
                               "Japan" = "#E9D8A6",
                               "Germany" = '#A3C4F3',
                               "India" = "#0077cc",
                               "United Kingdom" = "#FDE4CF",
                               "France" = "lightgrey",
                               "Russia" = "#94D2BD",
                               "Italy" = "darkgrey",
                               "Canada" = "#F9C74F")) +
  geom_text(data = . %>% filter(Country %in% c("India", "China", "United States")), 
            aes(label = round(Values)), hjust = 1.2, color = "white", fontface = "bold", size = 3) + 
  labs(x = "POPULATION, 2022 in millions",
       size = 5, fontface = 'bold') +
  scale_x_continuous(breaks = c(0,800,1500), limits = c(0,1500)) +
  theme_minimal() +
  theme(axis.title.x = element_text(face = "bold"),
        axis.text.y = element_text(face = 'bold'),
        axis.title.y = element_blank(),
        legend.text = element_text(size = 7),
        legend.position = "none",
        panel.grid.major.y = element_blank(),
        axis.ticks.x = element_line(size = 2),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold")
  )

combined_plots <- p5 + p6 +
  plot_layout(ncol = 2, widths = c(3, 1))

print(combined_plots)

```

------------------------------------------------------------------------

###### Beyond sheer GDP numbers, economic prosperity requires a look at per-capita incomes

<p style="font-size: 16px;">Tracking top 10 countries on per-capita GDP, A comparison among peers</p>

<p style="font-size: 14px;"> Source: IMF's World Economic Outlook, Oct 2023</p>

```{r}

NGPDPC <- read_excel("data/NGPDPC.xlsx")

NGPDPC_long <- pivot_longer(NGPDPC, 
                            cols = `2001`:`2022`, 
                            names_to = "Year", 
                            values_to = "NGDPDPC")



NGPDPC_long$Year <- as.numeric(NGPDPC_long$Year)

NGPDPC_long %>%
  ggplot(aes(x = Year, y = NGDPDPC, color = Country, 
               group = Country)) +
  geom_line() +
  geom_point(data = function(x) subset(x, 
                                       Year == max(Year)), 
             aes(group = Country), size = 8) +
  annotate("text", x = 2022, y = 90000, 
           label = "Per-capita Rank", 
           size = 4, 
           color = "#064E40", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("text", x = 2028, y = 90000, 
           label = "GDP Rank", 
           size = 4, 
           color = "#0d98ba", 
           fontface = "bold",
           check_overlap = TRUE) +
  annotate("point", x = 2028, y = 76650.250, 
           size = 8, color = "#CA6702") +
  annotate("text", x = 2025.2, y = 76650.250, 
           label = "United States", 
           size = 4, 
           color = "#CA6702", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("text", x = 2022, y = 76345.250, 
           label = "1", 
           size = 4, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("text", x = 2028, y = 76345.250, 
           label = "1", 
           size = 4, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("text", x = 2025.2, y = 12669.620, 
           label = "China   ", 
           size = 4, 
           color = "#ff9900", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("point", x = 2028, y = 12669.620, 
           size = 8, color = "#ff9900") +
  annotate("point", x = 2022, y = 12669.620, 
           size = 8, color = "#ff9900") +
  annotate("text", x = 2022, y = 12669.620, 
           label = "9", 
           size = 4, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("text", x = 2028, y = 12669.620, 
           label = "2", 
           size = 4, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("text", x = 2025, y = 2391.870, 
           label = "India", 
           size = 4, 
           color = "#0077cc", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("text", x = 2022, y = 2391.870, 
           label = "10", 
           size = 4, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE) + 
  annotate("point", x = 2028, y = 2391.870, 
           size = 8, color = "#0077cc") +
  annotate("text", x = 2028, y = 2391.870, 
           label = "5", 
           size = 4, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE) + 
  scale_x_continuous(breaks = c(2001, 2011, 2022), limits = c(2001, 2030)) + 
  scale_y_continuous(labels = scales::dollar_format(prefix = "$", 
                                                    suffix = "", 
                                                    big.mark = ","), 
                     breaks = c(0, 40000, 80000), limits = c(0,90000)) +
  scale_color_manual(values = c("United States" = "#CA6702",
                                "China" = "#ff9900",
                                "Japan" = "#E9D8A6",
                                "Germany" = '#A3C4F3',
                                "India" = "#0077cc",
                                "United Kingdom" = "#FDE4CF",
                                "France" = "lightgrey",
                                "Russia" = "#94D2BD",
                                "Italy" = "darkgrey",
                                "Canada" = "#F9C74F")) +
  theme_minimal() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.title.x = element_blank(), 
    axis.title.y = element_text(face = "bold"), 
    axis.ticks.x = element_line(size = 2),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5,
                               size = 8, margin = margin(r = -25)),
    legend.position = 'none',
    plot.title = element_text(face = "bold")
  ) +
  labs(y = "PER-CAPITA GDP ($)")

```

------------------------------------------------------------------------

##### Not all countries have had the same trajectory in Inflation, so is it right to compare countries based on GDP?

<p style="font-size: 16px;"> Inflation across countries (% change)</p>



```{r}
p1 <- dataPivot %>%
  filter(SbjCode == 'PCPIPCH', Country %in% c('Japan', 'China')) %>%
  ggplot(aes(y = Values, x = Year, group = interaction(Country, Segment), 
             color = Country)) +
  geom_smooth(method = "loess", se = FALSE) +
  labs(y= "INFLATION RATE(%)") +
  theme_minimal() + 
  scale_x_discrete(breaks = c(2001, 2011, 2022)) +
  scale_y_continuous(limits = c(-5,25)) +
  scale_color_manual(values = c("United States" = "#CA6702",
                                "China" = "#ff9900",
                                "Japan" = "#E9D8A6",
                                "Germany" = '#A3C4F3',
                                "India" = "#0077cc",
                                "United Kingdom" = "#FDE4CF",
                                "France" = "lightgrey",
                                "Russia" = "#94D2BD",
                                "Italy" = "darkgrey",
                                "Canada" = "#F9C74F"))+
  theme(legend.position = c(0.809, 0.945),  
        legend.box.background = element_rect(color = "grey"),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.spacing.y = unit(0.2, "cm"),
        legend.key.width = unit(1, "cm"),  
        legend.key.height = unit(0.5, "cm"), 
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.ticks.y = element_line(size = 2), 
        axis.title.y = element_text(face = "bold"), 
        axis.title.x = element_blank(),
        axis.ticks.x = element_line(size = 2)
  )


# India and Russia similar trajectories
p2 <- dataPivot %>%
  filter(SbjCode == 'PCPIPCH', Country %in% c('India', 'Russia')) %>%
  ggplot(aes(y = Values, x = Year, group = interaction(Country, Segment), 
             color = Country)) +
  geom_smooth(method = "loess", se = FALSE) +
  theme_minimal() + 
  scale_x_discrete(breaks = c(2001, 2011, 2022)) +
  scale_y_continuous(limits = c(-5,25)) +
  labs( x = 'YEAR', fonftace = 'bold') +
  scale_color_manual(values = c("United States" = "#CA6702",
                                "China" = "#ff9900",
                                "Japan" = "#E9D8A6",
                                "Germany" = '#A3C4F3',
                                "India" = "#0077cc",
                                "United Kingdom" = "#FDE4CF",
                                "France" = "lightgrey",
                                "Russia" = "#94D2BD",
                                "Italy" = "darkgrey",
                                "Canada" = "#F9C74F")) +
  theme(legend.position = c(0.803, 0.945),  # Adjust legend position
        legend.box.background = element_rect(color = "grey"),  # Add border around legend
        legend.text = element_text(size = 8),  # Adjust legend text size
        legend.title = element_text(size = 8),  # Adjust legend title size
        legend.spacing.y = unit(0.2, "cm"),  # Increase vertical spacing between legend items
        legend.key.width = unit(1, "cm"),  # Adjust the width of the legend key
        legend.key.height = unit(0.5, "cm"),  # Adjust the height of the legend key
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.title.x = element_text(face = "bold"),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_line(size = 2)
        )

# Rest of top 10 have similar
p3 <- dataPivot %>%
  filter(SbjCode == 'PCPIPCH', Country %in% c('United Kingdom', 'United States',
                                              'Canada', 'France', "Germany",
                                              'Italy')) %>%
  ggplot(aes(y = Values, x = Year, group = interaction(Country, Segment), 
             color = Country)) +
  geom_smooth(method = "loess", se = FALSE) +
  theme_minimal() + 
  scale_x_discrete(breaks = c(2001, 2011, 2022)) +
  scale_y_continuous(limits = c(-5,25)) +
  scale_color_manual(values = c("United States" = "#CA6702",
                                "China" = "#ff9900",
                                "Japan" = "#E9D8A6",
                                "Germany" = '#A3C4F3',
                                "India" = "#0077cc",
                                "United Kingdom" = "#FDE4CF",
                                "France" = "lightgrey",
                                "Russia" = "#94D2BD",
                                "Italy" = "darkgrey",
                                "Canada" = "#F9C74F")) +
  theme(legend.position = c(0.7146, 0.845),  # Adjust legend position
        legend.box.background = element_rect(color = "grey"),  # Add border around legend
        legend.text = element_text(size = 8),  # Adjust legend text size
        legend.title = element_text(size = 8),  # Adjust legend title size
        legend.spacing.y = unit(0.2, "cm"),  # Increase vertical spacing between legend items
        legend.key.width = unit(1, "cm"),  # Adjust the width of the legend key
        legend.key.height = unit(0.5, "cm"), # Adjust the height of the legend key
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.x = element_line(size = 2)
  )

(p1 + p2 + p3 ) +
  theme(plot.margin = margin(0.5, 1.8, 0.5, 0.5, "cm"))
```

------------------------------------------------------------------------

##### A complex yet compelling story - China's ascendancy in Purchasing Power Parity as it surpasses even US

<p style="font-size: 16px;">Plotting the comparative growth of Economies</p>



```{r}
fdat <- read_csv("data/percapitaPPP.csv")

fdatPiv <- pivot_longer(fdat, cols = '2001':'2022',
                        names_to = "Year",
                        values_to = "Values") %>%
  rename(SbjCode = 'WEO Subject Code') %>%
  select('Country', 'SbjCode', 'Year', 'Values')


fdatWide <- pivot_wider(fdatPiv, names_from = 'SbjCode',
                        values_from = "Values")

fdatWide$PPPGDP <- as.numeric(fdatWide$PPPGDP)
fdatWide$NGDPDPC <- as.numeric(fdatWide$NGDPDPC)


fdatWide %>%
  ggplot(aes(y = NGDPDPC,  x = PPPGDP, color = Country)) +
  geom_point(size = 1) +
  labs(
    x = "PURCHASING POWER PARITY GDP ($)",
    y = "PER-CAPITA GDP ($)"
  ) +
  # stat_smooth(method = 'auto', se = FALSE) +
  theme_minimal() +
  scale_x_continuous(breaks = c(0,30000), labels = c('0', '30k')) +
  scale_y_continuous(breaks = c(0,40000,80000), labels = c('0', '40K', '80K')) +
  scale_color_manual(values = c("United States" = "#CA6702",
                                "China" = "#ff9900",
                                "Japan" = "#E9D8A6",
                                "Germany" = '#A3C4F3',
                                "India" = "#0077cc",
                                "United Kingdom" = "#FDE4CF",
                                "France" = "lightgrey",
                                "Russia" = "#94D2BD",
                                "Italy" = "darkgrey",
                                "Canada" = "#F9C74F")) +
  theme(
    legend.position = 'none',
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.title.x = element_text(face = "bold"), 
    axis.title.y = element_text(face = "bold"), 
    axis.ticks.x = element_line(size = 2),
    axis.ticks.y = element_line(size = 2),
    axis.text.x = element_text(size = 8),
    plot.title = element_text(face = "bold")
  ) +
  facet_wrap(~ Country)

```

------------------------------------------------------------------------

##### Hello! World. Meet the actual real big economies

<p style="font-size: 16px;">Standings on Purchase Power Parity Terms, 2022</p>



```{r}

PPPdata <- read_excel("data/PPPdata.xlsx")

PPPdata %>%
  filter(Year == 2022) %>%
  ggplot(aes(y = NGDPDPC,  x = PPPGDP, color = Country, size = Country_Number)) +
  geom_point() +
  geom_text(data = . %>% filter(!(Country %in% c("China", "France", 
                                                 "Germany", "United Kingdom"))),
            aes(label = Country, 
                hjust = -0.3), 
            color = 'black',  # Specify text color here
            size = 3) +
  geom_text(data = . %>% filter((Country %in% c("China", "France", 
                                                "Germany", "United Kingdom"))), 
            aes(label = Country, 
                hjust = 1.3), 
            color = 'black',  # Specify text color here
            size = 3) + 
  labs(
    x = "PURCHASING POWER PARITY - GDP ($)",
    y = "PER-CAPITA - GDP ($)"
  ) +
  # stat_smooth(method = 'auto', se = FALSE) +
  theme_bw() +
  scale_y_continuous(breaks = c(0,25000,50000,75000)) +
  scale_x_continuous(breaks = c(0,10000,20000,30000)) +
  scale_color_manual(values = c("United States" = "brown",
                                "China" = "#ff9900",
                                "Japan" = "#E9D8A6",
                                "Germany" = '#A3C4F3',
                                "India" = "#0077cc",
                                "United Kingdom" = "#FDE4CF",
                                "France" = "lightgrey",
                                "Russia" = "#94D2BD",
                                "Italy" = "darkgrey",
                                "Canada" = "#F9C74F")) +
  theme(
    legend.position = 'none',
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.title.x = element_text(face = "bold"), 
    axis.title.y = element_text(face = "bold"), 
    axis.ticks.x = element_line(size = 2),
    axis.ticks.y = element_line(size = 2),
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 8),
    plot.title = element_text(face = "bold")
  ) +
  annotate("text", x = 25462.73, y = 76343.25, 
           label = "2", 
           size = 3, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE) +
  annotate("text", x = 30217.11, y = 12669.62, 
           label = "1", 
           size = 3, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE) +
  annotate("text", x = 11900.71, y = 2391.87, 
           label = "3", 
           size = 3, 
           color = "white", 
           fontface = "bold",
           check_overlap = TRUE)
```

------------------------------------------------------------------------

```{=html}
<style>
    .reveal .center {
        text-align: center;
        margin-top: 20vh; /* Adjust vertical positioning */
        margin-right: 20vh;
        font-size: 3em; /* Adjust font size */
    }
</style>
```

::: center
```         
Thank You!
```
:::
